\documentclass[12pt]{article}

\input{defaultPream}

%----------BEGIN SETUP----------

\section{Setup}

\qq We've elected to create the brand new system on one of Stefano's new
computers. That way, the current system is left untouched, and we are able to
play around freely. The current system is running Scientific Linux 5, so we are
installing the latest Scientific Linux, SL7, on the new testing computer. 

\qq SL7 has been cleanly installed, now to enable ssh. Turns out ssh is
installed and turned on by default in SL7, but it is unreachable via the WiFi; I
have to first ssh into NAS-1, then into the new computer.

\subsection{ROOT Installation}

\qq One of the most important pieces of software we're going to need is ROOT. I
installed the latest CentOS7 binary from root.cern.ch, and unpacked it. The
CentOS7 binary may be used on SL7 because they are both closely related. 

\subsection{Installing Stefano's Image}

\qq Stefano created a disk image for us before he left with DATE and SCRIBE
preinstalled and ready to go! It's at {\tt
  /nas1/cmsgem/software/srs_centos7_2.vdi}. Unfortunately, it's a {\tt vdi} file
rather than an {\tt iso}, so some conversions need to be done. I'm performing
everything on the MTS development machine.

\qq First we need to install some packages: {\tt qemu} and {\tt tklpatch}.
Since {\tt vdi} files are VirtualBox images, we need to download VirtualBox to
get the conversion tools:

\begin{itemize}
  \item {\tt cd /etc/yum.repos.d}
  \item {\tt wget
      http://download.virtualbox.org/virtualbox/rpm/rhel/virtualbox.repo}
  \item {\tt yum --enablerepo=epel install dkms}
  \item {\tt yum install VirtualBox-5.1}
\end{itemize}

\qq Now that VirtualBox is installed, we can start converting! First, the {\tt
  vdi} needs to be converted into a {\tt vmdk}, {\tt VBoxManage clonemedium
  srs_centos7_2.vdi srs_centos7_2.vmdk --format VMDK}. Then, to a raw file, {\tt
  gemu-img convert -f vmdk srs_centos7_2.vmdk -O raw srs_centos7_2.raw}. Next,
the raw disk must be mounted as a loop device, but, since the image has multiple
partitions, some extra steps must be performed. 

\qq Since the image has partitions, it must be specially prepared for mounting,
{\tt loopdev=\$(sudo losetup --show -f srs_centos7_2.raw)}. The the command was
assigned to a variable, because its output will be used more than once. The tool
{\tt kpartx} needs to be installed, {\tt sudo yum install kpartx}, and used to
add mappings to the image's partitions, {\tt sudo kpartx -a \$loopdev}. Now, the
image is ready to be mounted. Create a mount point, {\tt mkdir
  srs_centos7_2.mount}, and mount the image {\tt sudo mount
  /dev/mapper/\$(basename \$loopdev)p1 srs_centos7_2.mount}. The image should be
visible from {\tt df -h}, and accessible via the route specified by {\tt df}.

\qq Now a copy may be made of the root file system of the image. Create a
directory for the file system, {\tt mkdir srs_centos7_2.rootfs}, then copy the
contents of the mounted file system to the new directory, {\tt sudo rsync -a -t -r -S
  -I srs_centos7_2.mount/ srs_centos7_2.rootfs}. Now that the mount point has
been copied over, the original may be unmounted. 

\qq Scratch that, we're just gonna put DATE on it. Stefano linked me to the CERN
forum thread where he asked Brian Dorney for help to do exactly what we're
trying to do. 

\qq The first thing we need to do is follow the setup instructions from
\url{http://linux.web.cern.ch/linux/centos7/docs/install.shtml}. The first thing
that must be done is the configuration of the AFS client. Unfortunately, the
necessary command, {\tt locmap} is not installed on our system, nor is it
available from any of the installed repositories. I found it and its
dependencies from the CERN's Linux website where all of its packages are hosted,
\url{http://linuxsoft.cern.ch/cern/centos/7/cern/x86_64/Packages/}.

\qq Once those RPMs are downloaded, they may be directly installed with {\tt
  rpm}, but that command will not automatically install dependencies. To ease
the installation process, a yum repository containing the RPMs can be created. A
new file, {\tt /etc/yum.repos.d/localCERN.repo} was created, and in it were
placed the lines: \\
{\tt [localCERN] # the name of the new repository} \\
{\tt baseurl = file://<full path to directory containing RPMs>} \\
{\tt enabled=1 # enable the repo be default} \\
{\tt gpgcheck=0 # disable package verification} \\
While disabling package verification is generally bad practice, we do not have
the keys necessary to properly install them. We also know where we got them
from, and they are locally installed, so, in this particular case, it should not
be a big deal.

\qq Now that the repo has been created, {\tt locmap} can be installed, {\tt sudo
  yum install locmap}. When the required command, {\tt sudo locmap --configure
  afs}, is run, it complains that it cannot connect to {\tt xldap.cern.ch} and
that the afs module is disabled. I've enabled the module with {\tt sudo locmap
  --enable afs} and tried again to see what would happen, and, while it failed
once again to connect to {\tt xldap.cern.ch}, it says that it configured
everything!

\qq The next step is to preconfigure the AFS client for CERN by configuring NTP,
which must be enabled, {\tt sudo locmap --enable ntp}. Now, it can be configured
with {\tt sudo locmap --configure ntp}. Next, the following modules must be
enabled using the same command as above: cvmfs, eosclient, kerberos, lpadmin,
nscd, sendmail, ssh, and sudo. A list of every available module and their
statuses can be viewed with, {\tt sudo locmap --list}. Now, they must all be
configured with, {\tt sudo locmap --configure all}. 

\qq Well, turns out the AFS stuff doesn't work, probably because we couldn't
connect to the server. Fortunately, we only needed AFS to get the CERN
repositories, {\tt yum-alice-daq.cc7_64.repo} and {\tt
  yum-alice-daq.slc6_64.repo}. I had grabbed {\tt yum-alice-daq.cc7_64.repo}
from another computer, but the SLC6 repo was nowhere to be found. This problem
was solved by creating the repo file myself by copying the CC7 file, and
changing the URLs to point to where the SLC6 RPMs ought to be located. The
contents of {\tt yum-alice-daq.cc7_64.repo} is: \\
{\tt [main]} \\
{\tt [alice-daq-cc7]} \\
{\tt name=ALICE DAQ software and dependencies - CC7/64/} \\
{\tt baseurl=http://cern.ch/alice-daq/yum-alice-daq.cc7_64/} \\
{\tt
  baseurl=https://yum:daqsoftrpm@alice-daq-yum.web.cern.ch/alice-daq-yum/cc7_64/}
\\
{\tt enabled=1} \\
{\tt protect=1} \\
{\tt gpgcheck=0} \\
The contents of the newly created {\tt yum-alice-daq.slc6_64.repo} is: \\
{\tt [main]} \\
{\tt [alice-daq-slc6]} \\
{\tt name=ALICE DAQ software and dependencies - slc6/64/} \\
{\tt baseurl=http://cern.ch/alice-daq/yum-alice-daq.slc6_64/} \\
{\tt
  baseurl=https://yum:daqsoftrpm@alice-daq-yum.web.cern.ch/alice-daq-yum/slc6_64/}
\\
{\tt enabled=1} \\
{\tt protect=1} \\
{\tt gpgcheck=0} \\

Running a quick {\tt sudo yum update} is helpful here, just double check to make
sure you're not accidentally installing any SLC6 packages. 

\qq Now to install a bunch of things from these repositories! The installation
instructions from here,
\url{https://alice-daq.web.cern.ch/products/date-installation-and-configuration}
were followed. 

\qq The first command {\tt rpm -e mysql-libs mysql mysql-devel
  postfix} produced some errors, but they are excusable. They appeared because
those packages simply are not installed on our machine; the {\tt postfix} one,
however, is. While simply {\tt rpm -e postfix} could have been executed with
equal affect, it is safe to include the other three packages in case they
happened to have been mysteriously installed onto the system. 

\qq The next command is {\tt rm -rf /var/lib/mysql/}, but that directory should
not exist in the first place, since MySQL is not installed. Now, we must install
a bunch of packages (including DATE!), {\tt sudo yum install BWidget
  MySQL-shared MySQL-client MySQL-devel dim smi tcl-devel tk-devel curl-devel
  libxml2-devel pciutils-devel mysqltcl xinetd ksh tcsh date}. With that
completed, MySQL server must be installed, {\tt yum install
  MySQL-server}. This time, a conflict with {\tt mariadb-libs} was encountered,
but we can just erase this package, since we don't need it, {\tt yum erase
  mariadb-libs}. 

\qq The next step is to setup MySQL. First the service must be started, {\tt
  service mysql start}. Since the root account must be setup first, and the
temporary root password is stored in root's home directory, we must switch to
root to complete setting up the initial account, {\tt sudo su}. The temporary
password is viewed with {\tt cat /root/.mysql_secret}. Copy that password, then
paste it when prompted after running, as root, {\tt mysqladmin -u root -h
  localhost -p password}. 

\qq Now that the root account has been created, the user accounts can be
added. You may log out of root. First the {\tt DATE_SITE} environment variable
must be cleared, {\tt unset DATE_SITE}, then the date setup script must be
executed, {\tt . /date/setup.sh}. Afterwards, the MySQL initialization script
must be executed to configure the new database, {\tt newMysql.sh}. While the
settings may be changed to whatever best fits the situation, the defaults are
sufficient.

\qq Now that the MySQL database is initialized, it must be configured, for DATE,
{\tt newDateSite.sh}. NOTE: To create the required {\tt /dateSite} directory, it
will ask for the root password. When prompted, confirm that a minimal
configuration is to be created; this is not the default setting. Also confirm
that all detectors are to be added and that all trigger class masks ought to be
added; these are not the default settings.

\qq With the base DATE configuration complete, the local configuration can
begin. These next few steps must be completed as root ({\tt sudo su}). The path
of the DATE_SITE must be set, {\tt export DATE_SITE=/dateSite}, the setup script
must be executed, {\tt . /date/setup.sh}, and the local configuration command
must be run, {\tt dateLocalConfig -s}.

\qq Running {\tt dateLocalConfig -s} will result in an error because, in
CentOS7, {\tt iptables} has fallen away in favor of {\tt firewalld}. These
instructions form StackOverflow,
\url{https://stackoverflow.com/questions/24756240/how-can-i-use-iptables-on-centos-7}
describe how to switch back from {\tt firewalld} to {\tt iptables} so that DATE,
built for SLC6, will be happy.

\qq First, {\tt firewalld} needs to be stopped,{\tt systemctl stop firewalld},
and hidden away, {\tt systemctl mask firewalld}. Next, {\tt iptables} must be
installed, {\tt yum install iptables-services}, and enabled, {\tt systemctl
  enable iptables} followed by {\tt systemctl start iptables}. Running {\tt
  dateLocalConfig -s} will, again, produce an error, but running it again
immediately will work, somehow.

\qq Next, the DIM (Distributed Information Management) name server must be
launched (and must be launched after each boot; this will be automated), {\tt
  /date/runControl/start_dim.sh &}. This returned a ``no process found'' error,
but running it again seemed to work fine. This error comes about because of
slightly different paths to {\tt do_start_dim.sh}, whose location can be found
with {\tt locate do_start_dim.sh}.

\qq The infoLoggerServer must also be started (these commands must be run after
each boot; this will be automated):\\
{\tt export DATE_SITE=/dateSite} \\
{\tt . /date/setup.sh} \\
{\tt /date/infoLogger/infoLoggerServer.sh start} \\

\qq The DAQ ought to be ready to be launched:\\
{\tt export DATE_SITE=/dateSite}\\
{\tt cd /date} \\
{\tt . ./setup.sh}\\
{\tt infoBrowser}\\
{\tt runControl/DAQCONTROL.sh}\\

\qq Now, it's time to install AMORE as root ({\tt sudo su}), {\tt yum install
  amore}. While all of the AMORE tools are installed, they are not part of the
{\tt PATH} environment variable, so they cannot be run by basename on the normal
prompt. Their install location can be found with {\tt locate amoreMysqlSetup},
which will display the full path to one of the tools. The remainder of the tools
are in the same directory. In our case, that directory is {\tt /opt/amore/bin/},
so that is what we will add to the {\tt PATH} variable, {\tt
  PATH=\$PATH:/opt/amore/bin}. Be sure to add {\tt export
  PATH=\$PATH:/opt/amore/bin} to both the user's and root's {\tt
  ~/.bash_profile}. Now all the AMORE tools are accessible by their
basenames.

\qq The next step is to set up the MySQL database for AMORE, {\tt amoreMysqlSetup}.
The defaults are sufficient. Now the AMORE site itself needs to be created, {\tt
  newAmoreSite}, and the defaults are fine. The problem with AMORE now is that
the {\tt amore} command, itself, does not work.

\qq The next step is to install the hardware drivers for the MTS
hardware. Unfortunately, that is proving difficult. The source for {\tt
  date-114} does not contain many of the required directories. {\tt date-100},
however, does, so we've uninstalled the latest version of DATE, and installed
the old version instead. We've followed all the instructions for configuring
DATE again, including rebuilding the MySQL database.

\qq We've come across our first issue: {\tt dateLocalConfig -s} is throwing some
{\tt xinetd} errors.

%-----------END SETUP-----------
